An MCM Paper Made by Team 1234567

### 2025-01-25 论文/PAPER.tex
上传题目
latex论文添加了label 2

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2506135]{easymcm}  % 载入 EasyMCM 模板文件
\problem{C}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
\usepackage{amsmath}

@@

% 此处填写摘要内容
\begin{abstract}

    Here is the abstract of your paper.

@@

\section{Data Preprocessing}
\subsection{Basic Data Preprocessing}
\subsection{Data Mining}
\section{Task1:}
\subsubsection{Details about Model 1}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

@@

@@

% 长表格示例，更多用法请参考 longtable 宏包文档
% 以下环境及对应参数可实现表格内的自动换行与表格的自动断页
% 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
\begin{longtable}{ p{4em} p{14em} p{14em} }
\caption{Basic Information about Three Main Continents (scratched from Wikipedia)}
\label{tb:longtable}\\
\toprule
Continent & Description & Information \\
\midrule
Africa & Africa Continent is surrounded by the Mediterranean Sea to the
north, the Isthmus of Suez and the Red Sea to the northeast, the Indian
Ocean to the southeast and the Atlantic Ocean to the west. &
At about 30.3 million km$^2$ including adjacent islands, it covers 6\%
of Earth's total surface area and 20\% of its land area. With 1.3
billion people as of 2018, it accounts for about 16\% of the world's
human population. \\
\midrule
Asia & Asia is Earth's largest and most populous continent which
located primarily in the Eastern and Northern Hemispheres.
It shares the continental landmass of Eurasia with the continent
of Europe and the continental landmass of Afro-Eurasia with both
Europe and Africa. &
Asia covers an area of 44,579,000 square kilometres, about 30\%
of Earth's total land area and 8.7\% of the Earth's total surface
area. Its 4.5 billion people (as of June 2019) constitute roughly
60\% of the world's population. \\
\midrule
Europe & Europe is a continent located entirely in the Northern
Hemisphere and mostly in the Eastern Hemisphere. It comprises the
westernmost part of Eurasia and is bordered by the Arctic Ocean to
the north, the Atlantic Ocean to the west, the Mediterranean Sea to
the south, and Asia to the east. &
Europe covers about 10,180,000 km$^2$, or 2\% of the Earth's surface
(6.8\% of land area), making it the second smallest
continent. Europe had a total population of about 741 million (about
11\% of the world population) as of 2018. \\
\bottomrule
\end{longtable}

>>>>

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2506135]{easymcm}  % 载入 EasyMCM 模板文件
\problem{C}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
\usepackage{amsmath}
\usepackage{tabularray}

@@

% 此处填写摘要内容
\begin{abstract}
    Here is the abstract of your paper.

@@

\section{Data Preprocessing}
\subsection{Basic Data Preprocessing}
\subsection{Data Mining}
\section{Task1:}
\subsection{Details about Model 1}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

@@

%Table 2 : Variable Name
\begin{longtblr}[
	caption = {Variable Name},
	]{
		vline{1-4} = {1-10}{},
		hline{1-11} = {1-3}{},
	}
	Variable Name                                                    & \textit{Code}                                                & Definition                                                                      &  \\
	Whether~Host Country                                             & \textit{is host}                                             & {Whether the country is the host(1 for host,0 for\\~non-host)}                  &  \\
	{Medal Expectation\\Increment *Personnel\\Expectation lncrement} & {\textit{medal\_increment *}\\\textit{personnel\_increment}} & {Product of medal\\expectation increment and\\personnel expectation\\increment} &  \\
	{Sport Advantage\\Coefficient}                                 & \textit{sport\_adv}                                           & {Advantage coefficient of\\a specific sport}                                  &  \\
	Country Level                                                    & \textit{country\_lvl}                                        & {The level of the country in the competition\\(ordered by rank)}                &  \\
	{Project Medal\\Expectation /Project\\Personnel Expection~}                         & \textit{sport\_medal \_per\_ person}                          & {Ratio of sport medals to projected personnel\\for a specific sport}          &  \\
	Gold Medal Probability                                           & \textit{gold\_prob}                                          & {Probability of an athlete~\\winning a gold medal}                              &  \\
	{Silver Medal\\Probability}                                      & \textit{silver\_prob}                                        & Probability of an athlete~ winning a silver medal                               &  \\
	{Bronze Medal\\Probability}                                      & \textit{silver\_prob}                                        & Probability of an athletewinning a bronze medal                                 &  \\
	No Medal Probability                                             & \textit{no\_medal\_probe}                                    & Probability of an athlete winning no medal                                      &  \\
	&                                                              &                                                                                 &  \\
	&                                                              &                                                                                 &  
\end{longtblr}

@@

% 长表格示例，更多用法请参考 longtable 宏包文档
% 以下环境及对应参数可实现表格内的自动换行与表格的自动断页
% 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
